Automated Topic Naming

### 2012-01-17 ese/ese.tex
affiliation update
**  5. What about developer style    5. Reviewer 4 raises the some observed results may simply be due to    the differences among developer styles and not necessarily    reflecting different types of work.    - re: We added developer style threats to the end of the section:      Do different developers work on different NFRs?    - re: We added this concern to threats to validity.    - [X] Add to threats to validity.    - [X] Warn up front about developer style    - [X] Cite large changes paper that style can be an issue

\institute{
  Abram Hindle \at 
  Dept. of Computer Science\\
  University of Alberta\\
  Edmonton, AB, CANADA\\
  \email{abram@softwareprocess.es}
\and
  Neil A. Ernst \at
  Dept. of Computer Science\\
  University of British Columbia\\
  Vancouver, BC, CANADA\\
  \email{nernst@cs.ubc.ca}
\and
  Michael W. Godfrey \at
  David Cheriton School of Computer Science\\
  University of Waterloo\\
  Waterloo, Ontario, CANADA\\
  \email{migod@uwaterloo.ca}
\and 
  John Mylopoulos \at
  Dept. Information Eng. and Computer Science\\
  University of Trento\\
  Trento, ITALY\\
  \email{jm@disi.unitn.it}
}

@@

@@

>>>>

\institute{
  Abram Hindle \at 
  Dept. of Computing Science\\
  University of Alberta\\
  Edmonton, AB, CANADA\\
  \email{abram@softwareprocess.es}
\and
  Neil A. Ernst \at
  Dept. of Computer Science\\
  University of British Columbia\\
  Vancouver, BC, CANADA\\
  \email{nernst@cs.ubc.ca}
\and
  Michael W. Godfrey \at
  David Cheriton School of Computer Science\\
  University of Waterloo\\
  Waterloo, Ontario, CANADA\\
  \email{migod@uwaterloo.ca}
\and 
  John Mylopoulos \at
  Dept. Information Eng. and Computer Science\\
  University of Trento\\
  Trento, ITALY\\
  \email{jm@disi.unitn.it}
}

@@

One potential confound for this analysis is that we could be
describing developer style instead of developer focus. Developer style
would be a developers likelihood to use or not use terms found within
our dictionaries and training corpus. Further more a top developer, in
terms of frequency of commits, will have more samples and more likely
take on a more general role. We found in a previous
paper~\cite{largechanges} that often the words used to describe a commit
and the actual author of the commit were often correlated. Thus based
on that observation developer style might be a confounding concern.

@@

Developer style is another confounding issue, if we are searching for
these words we are relying on developers to use these words. This
study might be exploiting the behaviour or style of a few
developers. If one developer did not describe their commits well or
used fewer terms it is likely they would be associated with a NFR
topic regardless of the actual purpose of their commits.
